\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-17 papers/intro_paper/results_synthetic.tex
changes up to Sec. III

Finally, we investigate the impact on the estimation of \ab{the} GR parameters
\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
magnitude of deviation in the non-GR parameters. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. We summarise the results in
Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. Since the
measurement of the frequency and damping time in the $\pSEOB$ model
incorporate information from the masses and spins through the NR
fitting formulae (as shown in
Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
expected correlations between the mass, spins and the QNM frequencies,
leading to biased estimates in the masses and spins. We confirm here
that is not the case. \comment{AB: I don't see how from the figure O 
conclude that there are no correlations between masses/spins and QNMs.}

@@

Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
We choose an asymmetric system to increase the SNR in the higher modes.
We also choose the distance and orientation of the binary
such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during during the first three observing runs, 
such asymmetric and loud signals are no longer just a theoretical
prediction, but quite plausible at design sensitivities. Using this
signal, we attempt to measure both the $(2,\pm 2)$ and
$(3,\pm 3)$ QNMs. For this injected signal the SNR in
other sub-dominant modes is too low to be able to measure them.

We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the injection parameters, the predicted values of the $(2,\pm 2)$ and $(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68 ms)}  and \macro{(271.21 Hz, 4.50 ms)} respectively. The left panel of Fig.~\ref{fig:nohair_sxs} shows that the two-dimensional posteriors on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the predictions for a BBH merger in GR, indicated by the black plus sign.  Using fitting formulae provided in ~\cite{Berti:2005ys}, specifically,  Eqs. 2.1, E1, E3 and tables VIII and IX for the fitting coefficients, we infer the two-dimensional posterior probability distirbution on the final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red) QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two independent estimates are consistent with each other and correspond to a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)} indicated by the plus sign. As a consequence, this may be considered as a test of the no-hair conjecture. For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place. However, it might also be possible to combine information from multiple observation over the coming few years to obtain meaningful constraints on the $(3,\pm 3)$ and
other sub-dominant QNMs.

>>>>

Finally, we investigate the impact on the estimation of \ab{the} GR parameters
\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
magnitude of deviation in the non-GR parameters. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. We summarise the results in
Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. Since the
measurement of the frequency and damping time in the $\pSEOB$ model
incorporate information from the masses and spins through the NR
fitting formulae (as shown in
Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
expected correlations between the mass, spins and the QNM frequencies,
leading to biased estimates in the masses and spins. We confirm here
that is not the case. \comment{AB: I don't see how from the figure I can  
conclude that there are no correlations between masses/spins and QNMs.}

@@

Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
We choose an asymmetric system to increase the SNR in the higher modes.
We also choose the distance and orientation of the binary
such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
such asymmetric and loud signals are no longer just a theoretical
prediction, but quite plausible \ab{during O4.} \sout{at design sensitivities.} Using this
signal, we attempt to measure both the $(2,\pm 2)$ and
$(3,\pm 3)$ QNMs. For this injected signal the SNR in
other sub-dominant modes is too low to be able to measure them.

We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
injection parameters, the predicted values of the $(2,\pm 2)$ and
$(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68
  ms)} and \macro{(271.21 Hz, 4.50 ms)} respectively. The left panel
of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the
predictions for a BBH merger in GR, indicated by the black plus sign.
Using fitting formulae provided in Ref.~\cite{Berti:2005ys}, specifically,
Eq.~(2.1), Eq.~(E1) and Eq.~(E3) and Tables VIII and IX for the fitting coefficients,
we infer the 2D posterior probability distribution on the
final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red)
QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
independent estimates are consistent with each other and correspond to
a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)}
indicated by the plus sign. As a consequence, this may be considered
as a test of the no-hair conjecture. For most of the events observed
so far, the power in the $(3,\pm 3)$ has not been sufficient to
measure it along with the $(2,\pm 2)$, or in fact, in its
place. However, it might also be possible to combine information from
multiple observation over the coming few years to obtain meaningful
constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
